Something about correlation functions

### 2021-06-29 paper-correlations.tex
Write a section about execution time

getdata(side, :: Val{3}) =
    [value_noise(5x/side,
                 5y/side,
                 5z/side,
                 5, 34365) < 0.5
     for x in 1:side, y in 1:side, z in 1:side]
\end{verbatim}
An example of a two-dimensional image generated in this way is on
\cref{fig:valuenoise}. The function \code{getdata} generates the same image
sampled with different resolutions. For two-dimensional case we generate ten
arrays with the side of a square $s = 1000, 2000, \dots, 10000$ pixels and
measure execution time for each function. For three-dimensional case we measure
execution time for ten cubic arrays with the side $s = 50, 100, \dots, 500$. The
result for \code{Directional} module is on \cref{fig:timings}. All functions are
calculated with default values of optional arguments (that is: closed walls
boundary conditions and computation along axial directions).

@@

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d.png}
    \caption[]{{\small Two-dimensional case}}
    \label{fig:timings-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d.png}
    \caption[]{{\small Three-dimensional case}}
    \label{fig:timings-3d}
  \end{subfigure}
  \caption[]{\small Execution times for different functions from
    \code{Directional} module.}
  \label{fig:timings}
\end{figure*}
\twocolumngrid

>>>>

getdata(side, :: Val{3}) =
    [value_noise(5x/side,
                 5y/side,
                 5z/side,
                 5, 34365) < 0.5
     for x in 1:side, y in 1:side, z in 1:side]
\end{verbatim}
An example of a two-dimensional image generated in this way is on
\cref{fig:valuenoise}. The function \code{getdata} generates the same image
sampled with different resolutions.

To measure efficiency of \code{Directional} module we generate ten arrays with
a side of a square $s = 1000, 2000, \dots, 10000$ pixels for two-dimensional
case and ten arrays with a side of a cube $s = 50, 100, \dots, 500$ voxels for
three-dimensional case and calculate execution time for each function. All
functions are calculated with default values of optional arguments (that is:
closed walls boundary conditions and computation along axial directions).

To measure efficiency of \code{Map} module we follow the same procedure but with
seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
cubes with a side $s = 50, 100, \dots, 350$ voxels.

The measurements of execution time is on \cref{fig:timings}.

\textbf{TODO: alogithmic efficiency for two and three dimensions as a function
  of number of elements.}

@@

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d.png}
    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
    \label{fig:timings-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d.png}
    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
    \label{fig:timings-3d}
  \end{subfigure}
    \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-map.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}}}
    \label{fig:timings-2d-map}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-map.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}}}
    \label{fig:timings-3d-map}
  \end{subfigure}
  \caption[]{\small Execution times for different correlation functions.}
  \label{fig:timings}
\end{figure*}
\twocolumngrid
